Machine learning high multiplicity matrix elements for electron-positron and hadron-hadron colliders

### 2023-03-13 paper3.tex
chapter 7 parameters

\subsection{Generation of data}\label{sec:pp_data}
Data is generated using the {\Sherpa} event generator
with the {\Amegic} matrix element generator.
Below we list the selection criteria for the phase-space sampling.

@@

>>>>

\subsection{Generation of data}\label{sec:pp_data}
Data is generated using the {\Sherpa} event generator
with the {\Amegic} matrix element generator.
Below we list the selection criteria for the phase-space sampling and
document the parameters used for matrix element evaluation in Table~\ref{table:fame3_params}.

@@

\begin{table}[t]
    \centering
    \begin{tabular}{ll}
        \toprule
        Parameters & \\
        \midrule
        Scales & \makecell[l]{$\mu_{R} = \mu_{F} = 91.188$ GeV for $Z+$jets \\ $\mu_{R} = \mu_{F} = 175$ GeV for $t\bar{t}+$jets} \\
        \midrule
        Masses & \makecell[l]{$m_{d} = 0.01$ GeV \\ $m_{u} = 0.005$ GeV \\ $m_{s} = 0.2$ GeV \\ $m_{c} = 1.42$ GeV \\ $m_{b} = 4.8$ GeV \\ $m_{t} = 173.21$ GeV \\ $m_{e} = 0.511$ MeV \\ $m_{\mu} = 0.105$ GeV \\ $m_{\tau} = 1.777$ GeV \\ $m_{Z} = 91.1876$ GeV \\ $m_{W} = 80.385$ GeV \\ $m_{H} = 125$ GeV} \\
        \midrule
        Couplings & \makecell[l]{$\alpha_{s}$ set by PDF \\ $\alpha_{e} = 1/137.03599976$} \\
        \midrule
        Decay widths & \makecell[l]{$\Gamma_{t} = 2$ GeV \\ $\Gamma_{\tau} = 2.26735 \times 10^{-12}$ GeV \\ $\Gamma_{Z} = 2.4952$ GeV \\ $\Gamma_{W} = 2.085$ GeV \\ $\Gamma_{H} = 4.07 \times 10^{-3}$ GeV} \\
        \bottomrule
        \end{tabular}
    \caption{List of parameters for the matrix element generation. Masses and decay widths not listed explicitly have been set to zero.}
    \label{table:fame3_params}
\end{table}
